\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2020-01-16 R1/Response.tex

	    \textit{The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen.  Similarly, they compare with variance scaling without explaining what they mean by variance scaling.}\\

	    The shrinkage estimator is that of Sch\"afer and Strimmer~(2005). Details on this method (including the choice of shrinkage parameter) are now provided.  Similarly, we now provide more detail on variance scaling, which simply refers to using the variance of one step ahead in-sample forecast errors.\\

	    \textit{In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation. Maybe a second case study or a simulation study is needed to show the value of the geometric insights provided. We already know that MinT is better than OLS and WLS. What is the new and better reconciliation approach that has come from the geometric insights?}\\

		We now propose a generalised version of MinT, to be used with a loss function where $\bm{W}$ is defined by the context of the problem.  In our empirical study we provide one such example of a loss function.  We show that blah blah blah. TO DO (TAS).  Demonstrating these additional contributions in the context of our existing empirical example has lengthened the paper considerably.  Therefore, we prefer to refrain from including a second empirical demonstration.\\

@@

		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS always improves MSE, while this is not the case for the other reconciliation approaches. To gain a better understanding of the implications of Theorem 3.2, it would be useful to show that the other approaches always
		improve accuracy in their transformed spaces.}\\

	    Report results for two different error metrics and include this. TO DO\\

		\textit{What is the interpretation of the transformed spaces and can the authors make the connection	between these spaces and the choice of reconciliation approach and error measure more clear?}\\

	    Reflecting on this issue has led us towards the development of a generalised version of MinT which we now include in the paper.  Briefly, the geometric insight allows us to decouple the issue of choice of loss function (which may be influenced by the context of the forecasting problem) from the issue of the properties of a given reconciliation method (which is a statistical question).  TO DO (TAS).\\

### 2020-01-16 R1/Letter.tex
minor changes

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item blah
\end{enumerate}

>>>>

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We introduce a modification of MinT that can be used with a user defined loss function.  We demonstrate in the empirical example that...
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias), a Nemenyi evaluation to highlight where differences in forecast accuracy are significant.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
\end{enumerate}
